---
title: "Hahn lab protocols"
output:
  prettydoc::html_pretty:
    theme: architect
    toc: yes
  pdf_document:
    number_sections: yes
    toc: yes
fontsize: 18pt
---

Welcome to the Hahn lab protocols page. Here is a master list of lab procedures we use for gene and protein expression. Please visit [our lab page](http://entomology.ifas.ufl.edu/hahn/lab/) to find out more about our work. Click [here](https://github.com/adnguyen/Hahn_lab_protocols) for the github repository for this website.  

updated: 2017-12-22  

# Gene expression workflow   

```{r,echo=FALSE}
library(DiagrammeR)

mermaid("
graph TD
  a{Tissue} --> b(RNA Isolation) 
  b --> c[Quality Control] 
  c --> d[Reverse Transcription] 
  d --> e[quantitative real time PCR]
  e --> f[Data processing and handling]
")
```

## RNA isolation  

### Reagents:  

### Protocol: 


## RNA quantification and quality control   

## cDNA synthesis: reverse transcription    

## Quantitative Real Time PCR    

## Data processing and handling  

# Protein expression workflow   

```{r,echo=FALSE}
mermaid("
graph TD
  a{Tissue} --> b(Protein Isolation) 
  b --> c[Quality Control] 
  c --> d[Polyacrylamide Gel Electrophoresis] 
  d --> e[Western Blotting]
  e --> f[Data processing and handling]
")
```


## Protein Isolation   

### Reagents   

### Protocol 

## Quantifying protein and quality control   

## Polyacrylamide Gel Electrophoresis   

## Western Blotting  

## Data processing and handling 
