---
title: "Hahn lab protocols"
output:
  prettydoc::html_pretty:
    theme: architect
    toc: yes
  pdf_document:
    number_sections: yes
    toc: yes
fontsize: 18pt
---

Welcome to the Hahn lab protocols page. Here is a master list of lab procedures we use for gene and protein expression. Please visit [our lab page](http://entomology.ifas.ufl.edu/hahn/lab/) to find out more about our work. Click [here](https://github.com/adnguyen/Hahn_lab_protocols) for the github repository for this website.  

updated: 2017-12-22  

# Gene expression workflow   

```{r,echo=FALSE}
library(DiagrammeR)

mermaid("
graph TD
  a{Tissue} --> b(RNA Isolation) 
  b --> c[Quality Control] 
  c --> d[Reverse Transcription] 
  d --> e[quantitative real time PCR]
  e --> f[Data processing and handling]
")
```

## RNA isolation  

### Reagents:  

* [TRI Reagent](https://www.thermofisher.com/order/catalog/product/15596026) (cat# 15596026)
* [BCP(1-bromo-3-chloropropane)](https://www.fishersci.com/shop/products/bcp-47/nc9551474#?keyword=BCP)(cat# NC9551474)
* [THE RNA storage solution] (https://www.thermofisher.com/order/catalog/product/AM7001)(cat# AM7001)
* [DNA-free™ DNA Removal Kit] (https://www.thermofisher.com/order/catalog/product/AM1906) (cat# AM1906)
* [Qubit™ dsDNA BR Assay Kit] (https://www.thermofisher.com/order/catalog/product/Q32850) (cat# Q32850)
* [Qubit™ RNA IQ Assay Kit]  (https://www.thermofisher.com/order/catalog/product/Q33221?SID=srch-srp-Q33221) (cat# Q33221)
### Protocol: 

RNA isolation protocol (originated from Applied Biosystems and adpted to our lab condition) (https://assets.thermofisher.com/TFS-Assets/LSG/manuals/9738M_D.pdf)

Homogenize
1. Homogenize in 1ml TRI Reagent and 5 beads by the Bead Mill Homogenizer (Precellys® Evolution), use the soft tissue program which will homogenize 15s, break for 30s and then homogenize for an additional 15s.
2. Icubate the homogenates for 5 min at room temperature.

RNA extraction
3. Add 100 μL BCP per 1 mL of TRI Reagent solution,mix well, and incubate at room temp for 5–15 min.
4. Centrifuge at 12,000 x g for 10–15 min at 4°C, then transfer the aqueous phase to a fresh tube.

RNA Precipitation and Wash 
5. Add 500 μL of isopropanol per 1 mL of
TRI Reagent solution, vortex for 5–10 sec, and
incubate at room temp for 5–10 min.
6. Centrifuge at 12,000 x g for 8 min at 4–25°C, and
discard the supernatant.
7. Add 1 mL of 75% ethanol per 1 mL of

TRI Reagent solution.
8. Centrifuge at 7,500 x g for 5 min, remove the ethanol,
and vacum dry the RNA pellet for 5 min.

RNA Solubilization 
9. Dissolve RNA in the THE RNA storage solution.

## RNA quantification and quality control  
RNA concertration
1. the concentration of an RNA solution is determined by NanoDrop.

Dnase1 Treatment with DNA-free kit(https://www.thermofisher.com/order/catalog/product/AM1906) 


dsDNA contamination and RNA quality check


## cDNA synthesis: reverse transcription    





## Quantitative Real Time PCR    

## Data processing and handling  

# Protein expression workflow   

```{r,echo=FALSE}
mermaid("
graph TD
  a{Tissue} --> b(Protein Isolation) 
  b --> c[Quality Control] 
  c --> d[Polyacrylamide Gel Electrophoresis] 
  d --> e[Western Blotting]
  e --> f[Data processing and handling]
")
```


## Protein Isolation   

### Reagents   

### Protocol 

## Quantifying protein and quality control   

## Polyacrylamide Gel Electrophoresis   

## Western Blotting  

## Data processing and handling 
