---
title: "Hahn lab protocols"
output:
  prettydoc::html_pretty:
    theme: architect
    toc: yes
  pdf_document:
    number_sections: yes
    toc: yes
fontsize: 18pt
=======

Welcome to the Hahn lab protocols page. Here is a master list of lab procedures we use for gene and protein expression. Please visit [our lab page](http://entomology.ifas.ufl.edu/hahn/lab/) to find out more about our work. Click [here](https://github.com/adnguyen/Hahn_lab_protocols) for the github repository for this website.  

updated: 2017-12-22  

# Gene expression workflow   

```{r,echo=FALSE}
library(DiagrammeR)

mermaid("
graph TD
  a{Tissue} --> b(RNA Isolation) 
  b --> c[Quality Control] 
  c --> d[Reverse Transcription] 
  d --> e[quantitative real time PCR]
  e --> f[Data processing and handling]
")
```
## RNA isolation  

### Reagents:  

* [TRI Reagent](https://www.thermofisher.com/order/catalog/product/15596026) (cat# 15596026)
* [BCP(1-bromo-3-chloropropane)](https://www.fishersci.com/shop/products/bcp-47/nc9551474#?keyword=BCP)(cat# NC9551474)
* [THE RNA storage solution](https://www.thermofisher.com/order/catalog/product/AM7001) (cat# AM7001)
* [DNA-free™ DNA Removal Kit](https://www.thermofisher.com/order/catalog/product/AM1906) (cat# AM1906)
* [Qubit™ dsDNA BR Assay Kit](https://www.thermofisher.com/order/catalog/product/Q32850) (cat# Q32850)
* [Qubit™ RNA IQ Assay Kit](https://www.thermofisher.com/order/catalog/product/Q33221?SID=srch-srp-Q33221) (cat# Q33221)

### Protocol: 

RNA isolation protocol (originated from Applied Biosystems and adpted to our lab condition) (https://assets.thermofisher.com/TFS-Assets/LSG/manuals/9738M_D.pdf)

**Homogenize**   

1. Homogenize in 1ml TRI Reagent and 5 beads by the Bead Mill Homogenizer (Precellys® Evolution), use the soft tissue program which will homogenize 15s, break for 30s and then homogenize for an additional 15s.   

2. Icubate the homogenates for 5 min at room temperature.   

RNA extraction
3. Add 100 μL BCP per 1 mL of TRI Reagent solution,mix well, and incubate at room temp for 5–15 min.
4. Centrifuge at 12,000 x g for 10–15 min at 4°C, then transfer the aqueous phase to a fresh tube.

RNA Precipitation and Wash 
5. Add 500 μL of isopropanol per 1 mL of
TRI Reagent solution, vortex for 5–10 sec, and
incubate at room temp for 5–10 min.
6. Centrifuge at 12,000 x g for 8 min at 4–25°C, and
discard the supernatant.
7. Add 1 mL of 75% ethanol per 1 mL of

TRI Reagent solution.
8. Centrifuge at 7,500 x g for 5 min, remove the ethanol,
and vacum dry the RNA pellet for 5 min.

RNA Solubilization 
9. Dissolve RNA in the THE RNA storage soluStep 2: Remove contaminating DNA from RNA


## Remove contaminating DNA from RNA:
### Reagents:

*[Dnase1 Treatment with DNA-free kit](https://www.thermofisher.com/order/catalog/product/AM1906) 
*[HyClone™ Water, Molecular Biology Grade](https://www.fishersci.com/shop/products/hyclone-water-molecular-biology-grade-6/p-7058038#?keyword=molecular+grade+water)
0.5ml centrifuge tubes


### Protocol:
This protocol is for a 50ul reaction volume with up to 10ug RNA.

1.	Prepare the master mix as follows (prepare 5 tubes extra)
Dnase1 10× buffer       = 5.0ul (0.1× reaction volume) × (number of tubes+5)
Dnase1                        = 1.0ul × (number of tubes+5)
Molecular grade water = 4ul × (number of tubes+5)
2.	Pipette out 10ug RNA samples to new 0.5ml tubes (volume depends on the concentration of RNA samples), then add molecular grade water (volume=40ul-volume of RNA) to make the final volume to 40ul.

3.	Add 10ul master kit to each of the above reaction tube (now the total volume is 50ul)

4.	Incubate at 37˚C for 30min.

5.	Add 5ul (0.1× reaction volume) suspended DNase Inactivation Reagent and mix well.

6.	Incubate 2 min at room temperature. Mix every 30s to 60s (This step is very important in order to redisperse the DNase inactivation reagent.)

7.	Centrifuge at 10,000 × g for 1.5 min and transfer the RNA to a fresh tube.
Note: This centrifugation step pellets the DNase Inactivation Reagent. After centrifuging, carefully transfer the supernatant, which contains the RNA, into a fresh tube. Avoid introducing the DNase Inactivation Reagent into solutions that may be used for downstream enzymatic reactions, because it can sequester divalent cations and change the buffer conditions.
ion.




## RNA quantification and quality control  
RNA concertration
1. the concentration of an RNA solution is determined by NanoDrop.

Dnase1 Treatment with DNA-free kit(https://www.thermofisher.com/order/catalog/product/AM1906) 


dsDNA contamination and RNA quality check


## cDNA synthesis: reverse transcription    





## Quantitative Real Time PCR    

## Data processing and handling  

# Protein expression workflow   

```{r,echo=FALSE}
mermaid("
graph TD
  a{Tissue} --> b(Protein Isolation) 
  b --> c[Quality Control] 
  c --> d[Polyacrylamide Gel Electrophoresis] 
  d --> e[Western Blotting]
  e --> f[Data processing and handling]
")
```


## Protein Isolation   

### Reagents   

### Protocol 

## Quantifying protein and quality control   

## Polyacrylamide Gel Electrophoresis   

## Western Blotting  

## Data processing and handling 
